Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-11 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
reflexivity proof added

@@

In addition to the five axioms and three definitions that pertain specifically to the argument, the proof also uses {\bf S5}'s iteration principle (in the proof of Lemma 2) and the axiom of reflexivity for equality (in the proof of Theorem 1). The use of reflexivity could be avoided, but we chose to use it because it allows the construction of a shorter proof.

@@

\bibitem[{\itshape Benzm\"uller \& Brown \& Kohlhase(2004)}]{BenzmuellerBrownKohlhase}
Benzm\"uller, C. \& Brown C. \& Kohlhase, M. In: {\ishape Journal of Symbolic Logic}, Vol. 69, N. 4, pp. 1027--1088.

>>>>

\begin{lemma*}[Reflexivity]
$$
s=s
$$
\end{lemma*}

\begin{footnotesize}
\begin{prooftree}
\AXC{}\RightLabel{$1$}
\UIC{$P s$}\RightLabel{$\imp_I^1$}
\UIC{$P s\imp P s$}
\AXC{}\RightLabel{$2$}
\UIC{$P s$}\RightLabel{$\imp_I^2$}
\UIC{$P s\imp P s$}\RightLabel{$\wedge_I$}
\BIC{$P s\biimp P s$}\RightLabel{$\forall_I$}
\UIC{$\forall P. P s\biimp P s$}\dottedLine
\UIC{$s=s$}
\end{prooftree}
\end{footnotesize}

@@

In addition to the five axioms and three definitions that pertain specifically to the argument, the proof also uses {\bf S5}'s iteration principle (in the proof of Lemma 2) and the lemma of reflexivity for equality (in the proof of Theorem 1). The use of reflexivity could be avoided, but we chose to use it because it allows the construction of a shorter proof.

@@

\bibitem[{\itshape Benzm\"uller \& Brown \& Kohlhase(2004)}]{BenzmuellerBrownKohlhase}
Benzm\"uller, C. \& Brown C. \& Kohlhase, M. In: {\itshape Journal of Symbolic Logic}, Vol. 69, N. 4, pp. 1027--1088.
